### 2019-03-03 docs/notebooks/results.Rmd
write overly verbose linker/topic sentence for 'visual search' in intro

### Visual search tasks for investigating attention
In the "classical" form of the visual search paradigm [@wolfeVisualSearch1998], experimenters present a subject with a search display on which there are discrete items, i.e. objects. The subject is asked to report whether a target is present among distractors. The experimenter sets the probability that the target will be present on any given trial. Experimenters measure the reaction time and/or accuracy of the subjects. Often, the results are presented as a plot of reaction time as a function of set size (the number of discrete items in stimulus). By fitting a line to the plot of reaction times as a function of set size and taking the slope of that line, experimenters produced estimates of processing speed, i.e. "seconds per item". Slopes are almost horizontal when subjects are shown visual search stimuli where targets differ from distractors in some clearly salient **feature**, e.g. a red target among green distractors, and slopes become much steeper when targets differ from distractors in some harder-to-distinguish **spatial conjunction** of features, e.g., a digital 2 among digital 5s. Some examples of these stimuli are shown below, generated with https://github.com/NickleDave/searchstims.

>>>>

### Visual search tasks for investigating attention
In spite of the many attentional mechanisms proposed for neural networks, and the many parallels and links between studies of vision in psychology, neuroscience, and artificial intelligence, little work has been done to relate the tasks and models used to investigate visual attention to neural networks. Here we study the whether visual search tasks used to investigate attention and the different models of visual attention in the brain provide alternate ways of understanding existing CNNs, comparing their output with human behavior, and benchmarking new attentional mechansims.
We begin with background on visual search tasks. In the "classical" form of the visual search paradigm [@wolfeVisualSearch1998], experimenters present a subject with a search display on which there are discrete items, i.e. objects. The subject is asked to report whether a target is present among distractors. The experimenter sets the probability that the target will be present on any given trial. Experimenters measure the reaction time and/or accuracy of the subjects. Often, the results are presented as a plot of reaction time as a function of set size (the number of discrete items in stimulus). By fitting a line to the plot of reaction times as a function of set size and taking the slope of that line, experimenters produced estimates of processing speed, i.e. "seconds per item". Slopes are almost horizontal when subjects are shown visual search stimuli where targets differ from distractors in some clearly salient **feature**, e.g. a red target among green distractors, and slopes become much steeper when targets differ from distractors in some harder-to-distinguish **spatial conjunction** of features, e.g., a digital 2 among digital 5s. Some examples of these stimuli are shown below, generated with https://github.com/NickleDave/searchstims.
